Simulation study parametric

### 2025-03-17 R/simulation_study/local/parametric.Rmd
reorganize simulation study

@@

colnames(data_lf_he_prep)[colnames(data_lf_he_prep) %in% c("observed_BoundaryDistance","observed_BoundaryAngle")]<-
  c("BoundaryDistance","BoundaryAngle")
n_step=3

#compute spline interpolation
interpolation_data<-interpolate_BoundaryMetrics(data_lf_he_prep,response=c("y1","y2"),
                                                border,n_step,n_cores=6,k=0.5*nrow(data_lf_he_prep))

#create dataframe with interpolated values
interpolated_x_vec=as.vector(t(interpolation_data$x))
interpolated_y_vec=as.vector(t(interpolation_data$y))
interpolated_distance_vec=as.vector(t(interpolation_data$BoundaryDistance))
interpolated_angle_vec=as.vector(t(interpolation_data$BoundaryAngle))
interpolation_time=as.vector(t(interpolation_data$time))
ID=unlist(lapply(unique(data_lf_he_prep$ID), function(id) {
  n=nrow(data_lf_he_prep[data_lf_he_prep$ID==id,])
  rep(id,n*n_step)
}))

@@

crcvm_cubic_lf_he<- SDE$new(formulas = formulas,
                            data = data_lf_he_prep,type = "CRCVM_SSM",
                    response = c("y1","y2"),par0 = c(1,1,A,B,D0,D1,SIGMA_D,SIGMA_THETA),
                    fixpar=c("a","b","D0","D1","sigma_D","sigma_theta"),
                    other_data = list("H"=H,"interpolated_distance"=interpolation_data$BoundaryDistance,
                                              "interpolated_angle"=interpolation_data$BoundaryAngle))

@@

>>>>

formulas <- list(tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),a=~1,b=~1,D0=~1,D1=~1,sigma_D=~1,sigma_theta=~1)

@@

colnames(data_lf_he_prep)[colnames(data_lf_he_prep) %in% c("observed_BoundaryDistance","observed_BoundaryAngle")]<-
  c("BoundaryDistance","BoundaryAngle")
n_step=5

#compute spline interpolation
interpolation_data<-interpolate_BoundaryMetrics(data_lf_he_prep,response=c("y1","y2"),
                                                border,n_step,n_cores=6,df_ratio=0.95)

#create dataframe with interpolated values
interpolated_x_vec=as.vector(t(interpolation_data$y1))
interpolated_y_vec=as.vector(t(interpolation_data$y2))
interpolated_distance_vec=as.vector(t(interpolation_data$BoundaryDistance))
interpolated_angle_vec=as.vector(t(interpolation_data$BoundaryAngle))
interpolation_time=as.vector(t(interpolation_data$time))
ID=unlist(lapply(unique(data_lf_he_prep$ID), function(id) {
  n=nrow(data_lf_he_prep[data_lf_he_prep$ID==id,])
  rep(id,n*n_step)
}))

@@

#interpolated_distance[interpolated_distance==0] <- 0.05
crcvm_cubic_lf_he<- SDE$new(formulas = formulas,
                            data = data_lf_he_prep,type = "CRCVM_SSM",
                    response = c("y1","y2"),par0 = c(1,1,A,B,D0,D1,SIGMA_D,SIGMA_THETA),
                    fixpar=c("a","b","D0","D1","sigma_D","sigma_theta"),
                    other_data = list("H"=H,"interpolated_distance"=interpolation_data$BoundaryDistance,
                                              "interpolated_angle"=interpolation_data$BoundaryAngle))
crcvm_cubic_lf_he$update_lambda(c(1/0.5^2,1/0.5^2))

@@

```
```{r}

get_estimates<- function(sde,include_sigma_obs=FALSE) {

  post_coeff=sde$post_coeff(n_post=10000)
  post_par=list(
  "tau"=exp(post_coeff$coeff_fe[,"tau.(Intercept)"]),
  "nu"=exp(post_coeff$coeff_fe[,"nu.(Intercept)"]),
  "sigma_tau"=1/sqrt(exp(post_coeff$log_lambda[,"tau.s(ID)"])),
  "sigma_nu"=1/sqrt(exp(post_coeff$log_lambda[,"nu.s(ID)"])))

  if (include_sigma_obs) {
    post_par$sigma_obs=1000*exp(post_coeff$log_sigma_obs)
  }

  mean_par=lapply(post_par,mean)
  sd_par=lapply(post_par,sd)
  quant_par <- lapply(post_par,
                      quantile, probs = c(0.025, 0.975))

  return(list("estimates"=mean_par,"std.error"=sd_par,"quantiles"=quant_par))

}

get_estimates(crcvm_cubic_lf_he)
